Commutative Character Sheaves

### 2015-11-13 followup.tex
Added some todos

Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_G\otimes (\EE)_G$ by the diagram
\[
\begin{tikzcd}
m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{d}{c = m \circ (m \times (i \circ m \circ \theta))}  \arrow[dashed]{r} & (\EE)_G\otimes (\EE)_G\\
c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der}, \arrow{u}
\end{tikzcd}
\]
where the arrow labeled with the equation is the canonical isomorphism coming from the isomorphism of functors defined by the equation.
Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
$
m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
$
Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
\[
\begin{tikzcd}
\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
\end{tikzcd}
\]

@@

\begin{proof} 
Define
\begin{align*}
m_2 : G\times G\times G\times G &\to G\times G \\
(x_1,y_1,x_2,y_2) &\mapsto (x_1x_2, y_1y_2) \\
a_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
p_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2)
\end{align*}
and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}),
which comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$. 
This isomorphism satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
By abuse of notation, we will also refer to the missing vertical map down the center of this diagram as $\nu \boxtimes \nu$.  Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so we can reinterpret
\[
\mu : (\cs{L}_2, \mu_2, \nu_2) \to (\cs{L}\boxtimes\cs{L}, \mu \boxtimes \mu, \nu \boxtimes \nu)
\]
as a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

>>>>

Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_G\otimes (\EE)_G$ by the diagram \todo{Fix this diagram.}
\[
\begin{tikzcd}
m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{d}{c = m \circ (m \times (i \circ m \circ \theta))}  \arrow[dashed]{r} & (\EE)_G\otimes (\EE)_G\\
c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der}, \arrow{u}
\end{tikzcd}
\]
where the arrow labeled with the equation is the canonical isomorphism coming from the isomorphism of functors defined by the equation.
Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
$
m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
$
Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
\[
\begin{tikzcd}
\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
\end{tikzcd}
\]

@@

\begin{proof} 
Define
\begin{align*}
m_2 : G\times G\times G\times G &\to G\times G \\
(x_1,y_1,x_2,y_2) &\mapsto (x_1x_2, y_1y_2) \\
a_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
p_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2)
\end{align*}
and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}), \todo{False, because $m$ is not a group homorphism.}
which comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$. 
This isomorphism satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
By abuse of notation, we will also refer to the missing vertical map down the center of this diagram as $\nu \boxtimes \nu$.  Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so we can reinterpret
\[
\mu : (\cs{L}_2, \mu_2, \nu_2) \to (\cs{L}\boxtimes\cs{L}, \mu \boxtimes \mu, \nu \boxtimes \nu)
\]
as a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}
